\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{textcomp} % for \textasciitilde command
\usepackage{enumitem} 
\usepackage{bookmark}

\hypersetup{
    colorlinks=true,   % use colored text for links
    linkcolor=black,   % internal links
    urlcolor=black,    % URLs
    citecolor=black    % citations
}

\setlist[itemize]{topsep=-3pt, itemsep=-5pt, left=5pt}

\renewcommand*\familydefault{\sfdefault} 	

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\mytilde}[0]{
    \raisebox{0.5ex}{\texttildelow}
}
\name{Zephyr Serret}
\address{+32 470 85 10 51 \\ \href{mailto:zserret@me.com}{zserret@me.com} \\ \href{https://linkedin.com/in/zephyrsv}{linkedin.com/in/zephyrsv} \\ \href{https://github.com/ZephyrSV}{github.com/ZephyrSV}}  %

\begin{document}

%----------------------------------------------------------------------------------------
% EDUCATION 
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Universitat Politècnica de Catalunya \textendash{} UPC} \hfill {Sept 2019 \textendash{} Jan 2024}\\
Bachelor of Computer Science with Major in Computing \hfill {\it Barcelona, Spain} 

{\bf University of Edinburgh} \hfill {Sept 2022 \textendash{} Dec 2022}\\
{Erasmus \textendash{} Minor in Machine Learning}  \hfill {\it Edinburgh, UK\/}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

    \href{https://omp.com/}{\textbf{OM Partners}}           \hfill May 2024 \textendash{} Present \\
    \textit{Software Development Engineer} \hfill \textit{Antwerp, Belgium}
    \begin{itemize}
        \item {Tasked with solving performance and scalability issues in supply-chain planning application. Developed a multi-threaded, graph-based algorithm (C++20) which was deployed to end customers and integrated into the core optimization engine.}
        \item {Introduced new tooling and data-structures improving the codebase's debuggability, understandability and performance, landing me a spot in the company's C++ experts group.}
        \item {Automated fixes for recurring IDE issues and improved internal profiling tools.}
        \item {Challenged to debug a 40 year old codebase, 18000 KLOC and many interdependencies. Diagnosed and fixed performance bugs resulting in speedups in the magnitude of several hours.}
    \end{itemize}

    \textbf{SensingTex}                                     \hfill Jan 2023 \textendash{} Jul 2023 \\
    \textit{Junior FullStack developer} \hfill \textit{Barcelona, Spain}
    \begin{itemize}
        \item To meet the deadline for a new product launch, I developed and integrated new features and algorithms, resulting in a successful release.
        \item Led the development of the microcontroller firmware re-work (C++11), unifying the codebase across products and improving maintainability.
    \end{itemize}

    \textbf{Hewlett Packard \& UPC}                         \hfill Jan 2022 \textendash{} Aug 2022\\
    \textit{Software developer intern} \hfill \textit{Barcelona, Spain}
    \begin{itemize}
        \item {Worked on slicing software (C++17) for SLS 3D printers, implementing support for the new file format ".3mf".}
        \item I implemented triangle mesh optimization algorithms, reducing the slicing time for some meshes by 40\%.
    \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
    \vspace{-1.25em}
    \item \textbf{Bachelor Thesis} \hfill Jul 2023 \textendash{} Jan 2024 \\
    \href{https://github.com/ZephyrSV/tfg_python}{\it Orientating Biochemical reactions in metabolic pathways and Networks} \hfill {\it Barcelona, Spain} 
    \begin{itemize}
        \item { This study proposes an approach that utilizes ILP optimization to obtain a solution to the NP-hard problem of minimizing the number of external vertices in a hypergraph, in the context of Metabolic Pathways.}
    \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
% Achievements and Interests
%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements and Interests}
    \begin{itemize}
        \item \textbf{C++ Conferences} {CppOnSea UK 2025 (attendee), CppUnderTheSea Netherlands 2025 (volunteer).}
        \item \textbf{C++ in-person Workshops} {\textit{``Structured Concurrency in C++: A Hands-On Workshop''} by Mateusz Pusz, \\
        \textit{``C++ Software Design''} by Klaus Iglberger, \textit{``How to build a CUDA application in C++''} by NVIDEA.}
        \item \textbf{Hackathons} { Won 1st prize presented Optiver in HackUPC 2023. Won 2nd Prize in AdaHack 2022 Edinburgh.}
        \item \textbf{Teaching} {Led study group through HighSchool and University. Created the University class' discord Server.}
    \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages       & C++, C, C\#, Rust, Python, Java, Scala, Powershell, SQL, Javascript.\\
    Spoken Languages            & French (native), English (C2), Spanish (C2).\\
    Soft Skills                 & Autonomous-Learning, Leadership, Communication, Teamwork.\\
    Technical Skills            & Embedded Systems, Data Structures \& Algorithms, Multithreading, Git, REST APIs,\\
                                & (Non-)Relational Databases, Continuous Integration, Scalability, Testing.\\
    \end{tabular}\\

\end{rSection}

\end{document}